preciseTAD: A machine learning framework for precise TAD boundary prediction at base-level resolution

### 2020-08-26 Manuscript/manuscript.Rmd
Adjust figure location

@@

![**A diagram of the machine learning framework used to build domain boundary region prediction models.** Step 1 defines the dimensions of the data matrix $A_{N \times (p+1)}$ used for training and testing by establishing a resolution, $r$, at which to bin the linear genome into $N$ genomic bins for each chromosome, except a holdout chromosome *i*. The response vector **Y** is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$). A feature engineering procedure is selected to define the feature space of $A$ composed of $p$ genomic annotations. Step 2 is to reserve the predictor-response matrix for the holdout chromosome *i* as the test data. Step 3 is to apply a resampling technique to the training data to address the class imbalance. Step 4 is to train the random forest model and perform 3-fold cross-validation to tune for the mtry parameter. Finally, step 5 is to validate the model on the separate test data composed of the binned data from the holdout chromosome *i* and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)

>>>>

![**A machine learning framework for building domain boundary region prediction models.** Step 1 employs a range of feature engineering techniques to define defines the predictor matrix $A_{N \times (p)}$, where $N$ is the number of genomic bins, $p$ is the number of genomic annotations, $i$ is a holdout chromosome. The response vector $Y_N$ is defined as a boundary region ($Y=1$) if it overlaps with a genomic bin (else $Y=0$). Step 2 is reserves the predictor-response matrix for the holdout chromosome $i$ as the test data. Step 3 applies a resampling technique to the training data to address the class imbalance. Step 4 trains the random forest model and performs 3-fold cross-validation to tune the mtry parameter. Finally, step 5 validates the model on the separate test data composed of the binned data from the holdout chromosome $i$ and to evaluate model performance using balanced accuracy (BA).](Figures/figure2.png)

@@
